Expected Dependency Pair Match:\\ Predicting {HTER} improvements with expected syntactic structure

### 2009-05-11 mtjournal.tex
added some r confidence intervals, cleaned up intro to tuning

Table~\ref{tab:hterpersent} presents correlations weighted by sentence
length.  Though many of the $r$ values are smaller magnitude in this
correlation, EDPM again has the largest correlation in each category.
TER, however, does quite well with length-weighted sentence
correlation, with $r$ values within 95\% confidence of EDPM scores on
nearly every breakdown.

@@

In the previous section, we observed that TER and EDPM each perform
better than BLEU when considering mean-removed length-weighted
correlations with HTER.  We observe that TER's basic operations
(insertions, deletions, shifts and substitutions) are fundamentally
different from those of EDPM, which is an $F$-style overlap measure
and is seeking to make explicit comparison based on an inferred
syntactic structure.

TERp optimizer [Matt, a brief description here]

TERp comes with a variety of features (described earlier)

include optionally new features

Corpus: GALE 2.5 data, again documents randomly split into two groups,
evenly split across language and genre

tuning target: weighted correlation with mean-removed segment HTER

[we use weighted correlation to avoid emphasis on short segments
(which hurts document-level and system-level utility) ]

Select features from set:

\begin{description}
\item[E]: features from EDPM, specifically, P,R for inbound, outbound,
  full-links, and unlabeled links  (8 features)
\item[T]: features from basic TERp
  (inserts, deletes, substitutions, shifts)  (7 features)
\item[P]: features from TERp paraphraser
  (4 features)
\item[N]: precision and recall for 1-grams, 2-grams
\item[B]: brevity/prolixity (2 features: one for longer-than-ref, one for
  shorter-than-ref)
\end{description}

tune weights on one set, test on the other (and vice versa).
reporting average r between the two.

\begin{verbatim}
   == Tuned For Weighted Mean Removed Pearson
     - Examining WGT_MEAN_RM_SEG_PEAR ==
            Average
      Cond   Test  
     ---------------
      ETPB   0.4096
      ETP    0.4038
      TPB    0.4010
      TP     0.3946
      TPNB   0.3940
      TPN    0.3891
      ETB    0.3871
      ET     0.3827
      TB     0.3815
      ETNB   0.3814
      ETN    0.3804
      T      0.3758
      TNB    0.3708
      TN     0.3680
      E      0.3287
      EB     0.3267
      ENB    0.3149
      NB     0.3058
      EN     0.2973
      N      0.2636
      B      0.1638
\end{verbatim}
(maybe don't report all these numbers!)

@@

\appendix

[don't think we want an appendix]

>>>>

Table~\ref{tab:hterpersent} presents per-sentence correlations,
weighted by sentence length.  Though many of the $r$ values are
smaller magnitude in this correlation, EDPM again has the largest
correlation in each category.  TER, however, does quite well with
length-weighted sentence correlation, with $r$ values within 95\%
confidence of EDPM scores on nearly every breakdown.

@@

In the previous section, we observed that TER and EDPM each perform
better than BLEU when considering mean-removed length-weighted
correlations with HTER.  We observe that TER's basic operations
(insertions, deletions, shifts and substitutions) are fundamentally
different from those of EDPM, which is an $F$-style overlap measure
and is seeking to make explicit comparison based on an inferred
syntactic structure.  These two different approaches (word-level and
syntactic features) are complementary, and we seek in this section to
explore mechanisms for combining them.

As discussed in section~\ref{sec:intro}, the TER Plus (TERp) research
tools \cite{snover09terp} provide an optimizer for weighting multiple
simple subscores, including selecting weights for the TER basic
operations. TERp's feature list extends TER to additionally include
synonym tables and an empirically-derived paraphrase table.

TO DO: TERp optimizer [Matt, a brief description here]

In the experiments presented in this section, we extend this feature
list by including the syntactic overlap features, and we use the TERp
optimizer tools to tune the relative weight of each feature.

\subsection{Features}

We train a model using features from one or more of the following
sets:
\begin{description}
\item[E]: the fully syntactic features from the DPM family.
  Specifically, this featureset includes precision and recall scores
  for the $dl$, $lh$, $dlh$, and $dh$ decompositions of the syntactic
  structure, using $n=50$ and $\gamma=0.25$.  The \textbf{E} set
  includes 8 features.
\item[N]: the non-syntactic features from the DPM family;
  specifically, precision and recall for $1g$ and $2g$
  decompositions.  The \textbf{N} set includes 4 features.
\item[T]: the features from basic TERp, which include a separate cost
  for each of insertions, deletions, substitutions, shifts, and
  synonym-alignment. The \textbf{T} set includes 7 features.
  % TO DO: what are the other two?
\item[P]: features from the automatically-derived TERp paraphrase table
  (4 features)  % TO DO: Matt, what are these
\item[B]: two ``length penalties'' one is assigned the count of
  hypothesis words beyond the count of reference words, and one
  assigned the count of reference words beyond the count of hypothesis
  wordsbrevity/prolixity (2 features: one for longer-than-ref, one for
  shorter-than-ref)
\end{description}

For these tuning experiments we use the same GALE 2.5 documents and
sentences from the previous section.  Since this approach requires
tuning, we assign documents randomly into two groups, such that each
group has the same document distribution across source-language and
genre.
%
These two corpus halves are used in two-fold cross-validation, testing
on one and training on the other.  We tune on (and report correlation with)
length-weighted per-sentence correlation with HTER, using mean-removed
scores as before.

% tuning target: weighted correlation with mean-removed segment HTER

% [we use weighted correlation to avoid emphasis on short segments
% (which hurts document-level and system-level utility) ]
In table~\ref{tab:tuneresults}, we report the average $r$ between the
two.   
\begin{verbatim}
   == Tuned For Weighted Mean Removed Pearson
     - Examining WGT_MEAN_RM_SEG_PEAR ==
            Average
      Cond   Test  
     ---------------
      ETPB   0.4096
      ETP    0.4038
      TPB    0.4010
      TP     0.3946  > 0.416
      TPNB   0.3940
      TPN    0.3891
      ETB    0.3871
      ET     0.3827  > 0.404
      TB     0.3815  > 0.403
      ETNB   0.3814
      ETN    0.3804
      T      0.3758  > 0.398
      TNB    0.3708
      TN     0.3680  > 0.390
      TER    0.353   > 0.375
      E      0.3287  > 0.352
      EB     0.3267
      ENB    0.3149
      NB     0.3058  > 0.329
      EN     0.2973
      N      0.2636
      BLEU   0.244
      B      0.1638
\end{verbatim}
(maybe don't report all these numbers!)

TO DO: discuss this as a trend, despite lack of significance? plot charts?

@@

% \appendix

% [don't think we want an appendix]
